Algebraic Groups\vspace{-1ex}

### 2020-02-19 Algebraic Geometry/Algebraic-Geometry.tex
bump

>>>>

\section{February 19th}
Today Christine is talking!
\begin{lem}[Affine Communication Lemma]
	Let $\scrP$ be a property of some affines of a scheme $X$ such that
	\begin{enumerate}
		\item If $\Spec A\hookrightarrow X$ has $\scrP$ then for all $f\in A$, $\Spec A_f\hookrightarrow X$ has $\scrP$.
		\item If $(f_1,\dots,f_n)=A$ and $\Spec A_f\hookrightarrow X$ have $\scrP$ then $\Spec A\hookrightarrow X$ has $\scrP$.
	\end{enumerate}
	Further if $X=\cup_{i\in\scrI}\Spec A_i$ and the $\Spec A\hookrightarrow X$ have $\scrP$, then so does $X$.
\end{lem}

### 2020-02-19 Algebraic Groups/Algebraic-Groups.tex
bump

>>>>

\section{February 19th, 2020}
Welcome back! Today we're taking about the proof for that last problem (Frob. Reciprocity)
\begin{prf}
	Recall we have the map $\varepsilon_M:\Ind_H^G M\to M$, where we think of 
	\[\Ind_H^G M=(M\otimes k[G])^H=\{f:G\to M|h^{-1}f(-)=f(-\cdot h), gf(-)=f(g^{-1}\cdot -)\}\]
	and $\varepsilon_M(f)=f(1)\in M$. Then the map giving us our Frobenius reciprocity is just composing with $\varepsilon_M$.

	We will prove some of this. Let $\tilde\psi:N\to \Ind_H^G M$. Thus it corresponds, for each $n\in N$, to a map 
	\[\tilde\psi_n:G\to M\]
	and we need to define this map, check it is $H$-invariant, check that the resulting $\tilde\psi$ is $G$-invariant, and then check that this and $(\varepsilon_M\circ -)$ and this map are mutual inverses.

	Then we busted out paper and wrote stuff down. I checked $G$ invariance.
\end{prf}
\begin{cor}
	\begin{enumerate}
		\item $\Ind$ is transitive.
		\item $\Ind$ takes injectives to injectives.
	\end{enumerate}
\end{cor}
The way to prove this is to notice that it is a right adjoint to an exact functor.

\subsection{Projection formula}
\begin{thm}[Tensor identity/Projection formula]
	If $M\in\lmod H$ and $N\in\lmod G$,
	\[\Ind_H^G(M\otimes N)\simeq (\Ind_H^GM)\otimes N\]
\end{thm}
\begin{rmk}
	If $k$ is a ring instead of a field, we need to make an additional assumption: that $N$ is flat over $k$.
\end{rmk}
\begin{prf}
	We'll write down the maps at least. Since 
	\[L\eqdef \Ind_H^G(M\otimes N)=(M\otimes N\otimes k[G])^H\simeq\{f:G\to M\otimes N|f(gh)=(h^{-1}\otimes h^{-1})f(g)\}\]
	on the right, we have 
	\[R\eqdef\Ind_H^GM\otimes N=(M\otimes k[G])^H\otimes N\simeq\{f:G\to M\otimes N|f(xh)=(h^{-1}\otimes 1)f(x)\}\]

	Now we can write down two maps 
	\[\alpha,\beta:M\otimes N\otimes k[G]\to M\otimes N\otimes k[G]\]
	(thinking of these as maps $G\to M\otimes N$) in the following way:
	\[\alpha(f)(g)=(1\otimes g)f(g)\quad\text{and}\quad \beta(f)(g)(1\otimes g^{-1}f(g))\]
	and we claim:
	\begin{enumerate}
		\item $\alpha$ and $\beta$ are mutual inverses;
		\item $\alpha(L)=R$ and $\beta(R)=L$;
		\item $\alpha,\beta$ are $G$-invariant.
	\end{enumerate}
\end{prf}
\begin{rmk}
	This is a bit tedious, but this whole induction business is spelled out in Jantzen.
\end{rmk}

\subsection{What do we gain from all this?}
Well first, notice that $\Ind_e^G k=k[G]$, which implies taht $k[G]$ is injective. Then we have 
\begin{cor}
	Let $M\in \lmod k$ and notice 
	\[\Ind_e^G M\simeq\Ind_e^G(k\otimes k M)\simeq k[G]\otimes M_\text{triv}\]
	which is just a sum of copies of $k[G]$, which is again projective.
\end{cor}
\begin{cor}
	Let $M\in \Rep G$. Then 
	\[M\otimes k[G]\simeq M_\text{triv}\otimes k[G]\]
\end{cor}
\begin{prf}
	$M_\text{triv}\times k[G]\simeq\Ind_e^G M=\Ind_e^G(k\otimes M)\simeq \Ind_e^Gk\otimes M\simeq k[G]\otimes M.$
\end{prf}
\begin{rmk}
	The map between these things is nontrivial (we used some twisting in the tensor identity, for example). The map is 
	\[m\otimes f\mapsto (1\otimes f)(1\otimes S)\Delta_M(m)\]
	where $S$ is the coinverse.
\end{rmk}

\begin{thm}[``$\Rep G$ has enough injectives'']
	\begin{enumerate}
		\item $k[G]$ is injective.
		\item $\forall M\in\Rep G$, there is an injective $I$ with $M\hookrightarrow I$.
		\item Any injetive $I$ is a direct summand of $\bigoplus k[G]$.
	\end{enumerate}
\end{thm}
Corollary 2 gets us our injectives containing $M$. This sets us up to do homological algebra, which we will do next time.
